### 2025-07-09 short/sections/summary.tex
Update summary.tex

\textcolor{black}{In addition to research, I convene the undergraduate course Institutions of Governance and Development at Leiden University College and deliver doctoral lectures on data mining and AI at Universidad Diego Portales.}
\vspace{1mm}
\end{cvparagraph}

>>>>

\textcolor{black}{In addition to research, I teach the undergraduate course Institutions of Governance and Development at Leiden University College and deliver doctoral lectures on data mining and AI at Universidad Diego Portales.}
\vspace{1mm}
\end{cvparagraph}
